How fluid-mechanical erosion creates anisotropic porous media

### 2022-12-02 docs/PhysicsPaper/StokesErosion.tex
working on revisions

%\documentclass{jfm}
% NOTE: jfm documentclass needed for \upi
%---------------------------------------------------%
% Packages from JFM 2020
%\usepackage[top=1.2in,bottom=1.2in,left=1in, right=1in]{geometry}
\usepackage{amsfonts, amssymb, array}
\usepackage[fleqn,reqno]{amsmath}
\usepackage{graphics, graphicx, subfigure}
% Replaced subcaption with subfigure
\usepackage{todonotes, comment, soul, float}
%---------------------------------------------------%

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% COMMANDS
% Basic editing
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
\newcommand{\tocite}{ {\color{blue}(to cite)} }
\newcommand{\nick}[1]{ {\color{red} #1} }
\newcommand{\edit}[1]{ {\color{red} #1} }

@@

The outline of the paper is as follows. In Section~\ref{sec:formulation} we discuss the governing equations for the fluid flow and interface evolution. In Section~\ref{sec:DLP} we discuss the numerical methods, including the Cauchy formulation of the BIE. In Section~\ref{sec:medium} we explain how to extract porous-medium properties, such permeability, anisotropy, and tortuosity. In Section~\ref{sec:results} we provide results and we conclude in Section~\ref{sec:conclusion}.

%-----------------------------------------------------------------------------------------------%
\section{Governing Equations}
\label{sec:formulation}
%-----------------------------------------------------------------------------------------------%

@@

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%
To accurately and efficiently solve the Stokes equations~\eqref{eqn:StokesEq}, we reformulate the system as a boundary integral equation (BIE). A BIE formulation has the advantage that all the unknowns are on the one-dimensional boundaries of the domain. That is, only the boundary of the complex geometry must be discretized which we do with a spectrally accurate Fourier basis. Applying the same approach as our previous works~\cite{chiu2020viscous, quaife2018boundary}, we represent the velocity as the sum of a double-layer potential and a combination of Stokeslets and rotlets~\cite{pow-mir1987}
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + \sum_{\ell=1}^{M}\left(
    S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
    \quad \xx \in \Omega,
  \label{eqn:velocity}
\end{align}
where 
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
  \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
  \eeta(\yy) \, ds_\yy,
  \label{eqn:velocityDLP}
\end{align}
where $\rr = \xx - \yy$ and $\rho = \|\rr\|$. Note that $\bd\Omega$ includes both the eroding bodies and the outer boundary. The Stokeslets and the rotlets are
\begin{align}
  S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(-\log \rho_\ell +
  \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
  \quad
  R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
\end{align}
respectively, where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and $\cc_\ell$ is a point inside body $\ell$. If the density function, Stokeslets, and rotlets satisfy the second-kind boundary integral equation
\begin{subequations}
  \label{eqn:FredBIE}
  \begin{alignat}{3}
    \UU(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      \quad &&\xx \in \Gamma, \\
    \mathbf{0} &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      &&\xx \in \gamma_\ell, \: \ell = 1,\ldots,M, \\
    \llambda_\ell &= \int_{\gamma_\ell} \eeta(\yy) \, ds_\yy, 
      &&\ell = 1,\ldots,M, \\
    \xi_\ell &= \int_{\gamma_\ell} (\yy - \cc_\ell)^\perp \cdot 
      \eeta(\yy) \, ds_\yy, &&\ell = 1,\ldots,M,
  \end{alignat}
\end{subequations}
then the representation~\eqref{eqn:velocity} satisfies the Stokes equations with the required boundary conditions~\eqref{eqn:StokesEq}. We solve~\eqref{eqn:FredBIE} by discretizing $\gamma_\ell$ and $\Gamma$ at equispaced collocation points, and then replacing the integrals with quadrature rules. This results in a linear system with a mesh-independent condition number, and it is solved iteratively with GMRES.

Instead of evaluating the Stokes double-layer potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we convert the integral to a sum of contour integrals around Jordan curves in $\CC$. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_2$ and use similar notation for $\yy$, $\nn$, and $\eeta$. We also interpret $\gamma$, the boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan curve in $\CC$. We introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)),
\end{align}
and then define the five Cauchy integrals
\begin{align}
  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\gamma}
  \frac{\Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
\end{align}
Then, the first and second components of the Stokes double-layer
potential are
\begin{subequations}
  \begin{align}
    u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
             \Re(v_3'(x)) + \Re(v_4(x)) \\
    u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
             \Im(v_3'(x)) + \Re(v_5(x)),
  \end{align}
  \label{eqn:velocityCauchy}
\end{subequations}
respectively. The components of the deformation tensor are
\begin{subequations}
  \begin{align}
    \pderiv{u_1}{x_1} &= -\Re(v'_1(x)) + \Re(v''_3(x)) + \Re(v'_4(x))
                         -\Re(x)\Re(v''_1(x)) - \Im(x)\Re(v''_2(x)) \\
    \pderiv{u_1}{x_2} &= -\Re(v'_2(x)) - \Im(v''_3(x)) - \Im(v'_4(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_1} &= +\Im(v'_1(x)) - \Im(v''_3(x)) + \Re(v'_5(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_2} &= +\Im(v'_2(x)) - \Re(v''_3(x)) - \Im(v'_5(x))
                         +\Re(x)\Re(v''_1(x)) + \Im(x)\Re(v''_2(x)) 
  \end{align}
  \label{eqn:deformationCauchy}
\end{subequations}
Having the deformation tensor at hand, the vorticity can be shown to
satisfy
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
     \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
  \label{eqn:vorticityCauchy}
\end{align}
We note that the deformation tensor requires second-order derivatives of
Cauchy integrals, while the vorticity only requires first-order
derivatives. On solid boundaries, the vorticity reduces to the shear stress given in \eqref{tau0} and needed in errosion law \eqref{Vn0} \cite{quaife2018boundary, chiu2020viscous}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature for Cauchy integrals}
The overall accuracy of our method is determined by the
quadrature rule applied to equation~\eqref{eqn:FredBIE}. Since we have
written the Stokes double-layer potential
velocity~\eqref{eqn:velocityCauchy}, deformation
tensor~\eqref{eqn:deformationCauchy}, and
vorticity~\eqref{eqn:vorticityCauchy} as a sum of Cauchy integrals and
their derivatives, the overall accuracy hinges on the computation of a general Cauchy integral
\begin{align}
  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
  \label{eqn:cauchy1}
\end{align}
Here we describe a quadrature formulae that was first used to
approximate analytic functions~\cite{ioa-pap-per1991}, and then extended
to Stokes layer potentials~\cite{bar-wu-vee2015}. The quadrature method
requires the boundary data of the analytic function~\eqref{eqn:cauchy1}
which satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x_0-y} \, dy,
    \quad x_0 \in \gamma,
    \label{eqn:SP}
\end{align}
where the last integral is interpreted in the principal-value sense.
Here we are assuming that $\Omega$ is the bounded region interior to
$\gamma$. Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be
determined by its boundary data alone using the Cauchy Integral Theorem
\begin{subequations}
  \label{eqn:cauchy}
  \begin{alignat}{3}
  \label{eqn:cauchyv}
  v(x) &= \frac{1}{2\pi i}\int_{\gamma} 
    \frac{v^{-}(y)}{y-x} \,dy, \\
  v'(x) &= \frac{1}{2\pi i} \int_{\gamma}
    \frac{v^{-}(y)}{(y-x)^2} \, dy, \\
  v''(x) &= \frac{1}{\pi i} \int_{\gamma}
    \frac{v^{-}(y)}{(y-x)^3} \, dy.
  \end{alignat}
\end{subequations}

The trapezoid rule can be used to approximate this Cauchy integral and
its derivatives. For example, the Cauchy integral~\eqref{eqn:cauchyv}
can be approximated as
\begin{align}
  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^{N} 
    w_j \frac{v^{-}(y_j)}{y_j - x},
  \label{eqn:trap}
\end{align}
where $y_j$ are equispaced points on $\gamma$, $w_j = L/N$, and $L$ is
the length of $\gamma$. Because the integrand is both periodic and
smooth, given a fixed point $x$, the trapezoid rule achieves spectral
accuracy~\cite{tre-wei2014}. However, for a fixed $N$, the quadrature
error is not bounded uniformly with respect to $x$ because the
derivative of the integrand grows without bound as $x$ approaches
$\gamma$. This error is problematic for many of our simulations since we
allow eroding bodies to be arbitrarily close to one another, and we
often compute the velocity and vorticity at points in the fluid domain
that are close to an eroding body. In contrast to the integrand in the
Cauchy integral~\eqref{eqn:cauchyv}, the integrand in the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\gamma} 
    \frac{v^{-}(y) - v(x)}{y-x} \, dy = 0, \quad x \in \Omega,
  \label{eqn:trap2}
\end{align}
is bounded with respect to $x$, and therefore the error of the trapezoid
rule is bounded with respect to $x$. Applying the trapezoid rule, we
have
\begin{align}
  \frac{1}{2\pi i}\sum_{j=1}^{N} w_{j} 
    \frac{v^{-}(y_j) - v(x)}{y_j - x} \approx 0,
\end{align}
where the error is now uniformly bounded for all $x$. Rearranging, we
have
\begin{align}
  v(x) \approx \left(\frac{1}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}(y_j)}{y_j - x} w_j \right) \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j - x} w_j \right), 
  \quad x \in \Omega.
  \label{eqn:vBary}
\end{align}
Note that the numerator in~\eqref{eqn:vBary} is identical to
equation~\eqref{eqn:trap}, while the denominator is an approximation of
the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the errors
in the numerator and denominator grow, however, since the integrand in
equation~\eqref{eqn:trap2} is bounded independent of $x$, the error of
the ratio is also bounded independent of $x$.

The derivatives of the Cauchy integral in~\eqref{eqn:cauchy} can be
approximated with spectral accuracy, uniformly in $x$, using similar quadrature
rules. To summarize, for $x \in \Omega$, 
\begin{align}
  v'(x) &\approx \left(\frac{1}{2\pi i}\sum_{j=1}^{N}
    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j \right)
  \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^{N} \frac{1}{y_j-x} w_j\right), 
  \label{eqn:D1vBary} \\
  v''(x) &\approx \left(\frac{2}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j \right)
    \Bigg/
    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right),
  \label{eqn:D2vBary}
\end{align}
We note that equations~\eqref{eqn:vBary},~\eqref{eqn:D1vBary},
and~\eqref{eqn:D2vBary} all assume that $x \in \Omega$, where $\Omega$
is the bounded region interior to the Jordan curve $\gamma$. However, in
our application, when $\gamma$ is one of the eroding bodies, $x$ is in
the exterior region of the Jordan curve. In this case, slightly
different identities are used, but they all guarantee that the trapezoid
rule achieves spectral accuracy with an error that is independent of
$x$. A complete description of the quadrature rules
for~\eqref{eqn:vBary} and~\eqref{eqn:D1vBary} are described by Barnett,
Wu, and Veerapaneni~\cite{bar-wu-vee2015}, and the quadrature rule
for~\eqref{eqn:D2vBary} is described in our previous
work~\cite{chiu2020viscous}.

@@

%-----------------------------------------------------------------------------------------------%
\section*{Acknowledgements}
N.J.M., J.C., and B.D.Q. recognize the support of NSF Grant DMS-2012560
%-----------------------------------------------------------------------------------------------%

\bibliographystyle{plain}
\bibliography{refs}
\end{document}

>>>>

%\documentclass{jfm}
% NOTE: jfm documentclass needed for \upi
%---------------------------------------------------%
% Packages from JFM 2020
%\usepackage[top=1.2in,bottom=1.2in,left=1in, right=1in]{geometry}
\usepackage{amsfonts, amssymb, array}
\usepackage[fleqn,reqno]{amsmath}
\usepackage{graphics, graphicx, subfigure}
% Replaced subcaption with subfigure
\usepackage{todonotes, comment, soul, float}
\usepackage[title]{appendix}

%---------------------------------------------------%

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% COMMANDS
% Basic editing
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
\newcommand{\tocite}{ {\color{blue}(to cite)} }
\newcommand{\nick}[1]{ {\color{red} #1} }
\newcommand{\edit}[1]{{\color{red} #1}}

@@

The outline of the paper is as follows. In Section~\ref{sec:formulation}
we discuss the governing equations for the fluid flow and interface
evolution. In Section~\ref{sec:numerics} we discuss the numerical methods, including the Cauchy formulation of the BIE. In Section~\ref{sec:medium} we explain how to extract porous-medium properties, such permeability, anisotropy, and tortuosity. In Section~\ref{sec:results} we provide results and we conclude in Section~\ref{sec:conclusion}.

%-----------------------------------------------------------------------------------------------%
\section{Governing equations}
\label{sec:formulation}
%-----------------------------------------------------------------------------------------------%

@@

%-----------------------------------------------------------------------------------------------%
\section{\edit{Numerical methods}}
%\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:numerics}
%-----------------------------------------------------------------------------------------------%
\edit{To investigate the large-scale features of microscopic erosion, we
require numerical methods that are accurate in both space and time.
Section~\ref{sec:bie} reformulates the governing equations using a
boundary integral equation that is discretized with a spectrally
accurate quadrature rule, and Section~\ref{sec:int_evo} describes our
second-order numerical method for evolving the bodies. We note that the
numerical methods described in both sections require that the geometry
is two-dimensional. Extending our work to three dimensions requires
entirely different time quadrature formulas and time stepping methods.}

\subsection{\edit{Boundary integral equation formulation}}
\label{sec:bie}
To accurately and efficiently solve the Stokes equations~\eqref{eqn:StokesEq}, we reformulate the system as a boundary integral equation (BIE). A BIE formulation has the advantage that all the unknowns are on the one-dimensional boundaries of the domain. That is, only the boundary of the complex geometry must be discretized which we do with a spectrally accurate Fourier basis. Applying the same approach as our previous works~\cite{chiu2020viscous, quaife2018boundary}, we represent the velocity as the sum of a double-layer potential and a combination of Stokeslets and rotlets~\cite{pow-mir1987}
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + \sum_{\ell=1}^{M}\left(
    S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
    \quad \xx \in \Omega,
  \label{eqn:velocity}
\end{align}
where 
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
  \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
  \eeta(\yy) \, ds_\yy,
  \label{eqn:velocityDLP}
\end{align}
where $\rr = \xx - \yy$ and $\rho = \|\rr\|$. Note that $\bd\Omega$ includes both the eroding bodies and the outer boundary. The Stokeslets and the rotlets are
\begin{align}
  S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(-\log \rho_\ell +
  \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
  \quad
  R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
\end{align}
respectively, where $\rr_\ell = \xx - \cc_\ell$, \edit{$\rr_\ell^\perp =
(r_2,-r_1)$,} $\rho_\ell = \|\rr_\ell\|$, and $\cc_\ell$ is a point inside body $\ell$. If the density function, Stokeslets, and rotlets satisfy the second-kind boundary integral equation
\begin{subequations}
  \label{eqn:FredBIE}
  \begin{alignat}{3}
    \UU(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      \quad &&\xx \in \Gamma, \\
    \mathbf{0} &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      &&\xx \in \gamma_\ell, \: \ell = 1,\ldots,M, \\
    \llambda_\ell &= \int_{\gamma_\ell} \eeta(\yy) \, ds_\yy, 
      &&\ell = 1,\ldots,M, \\
    \xi_\ell &= \int_{\gamma_\ell} (\yy - \cc_\ell)^\perp \cdot 
      \eeta(\yy) \, ds_\yy, &&\ell = 1,\ldots,M,
  \end{alignat}
\end{subequations}
then the representation~\eqref{eqn:velocity} satisfies the Stokes
equations with the required boundary conditions~\eqref{eqn:StokesEq}. We
solve~\eqref{eqn:FredBIE} by discretizing $\gamma_\ell$ and $\Gamma$ at
equispaced collocation points, and then replacing the integrals with
quadrature rules. This results in a linear system with a
mesh-independent condition number, and it is solved iteratively with
GMRES. Instead of evaluating the Stokes double-layer
potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we
convert the integral to a sum of contour integrals around Jordan curves
in $\CC$. \edit{This conversion allows us to use quadrature formulas
whose errors are uniformly bounded independent of the proximity of the
bodies. Details of the conversion and the quadrature formulas are in
Appendix~\ref{appendix:A}.}

@@

%-----------------------------------------------------------------------------------------------%
\section*{Acknowledgements}
N.J.M., J.C., and B.D.Q.~recognize the support of NSF Grant DMS-2012560
%-----------------------------------------------------------------------------------------------%

\bibliographystyle{plain}
\bibliography{refs}

\begin{appendices}
\renewcommand{\theequation}{A.\arabic{equation}}
\setcounter{equation}{0}

\section{Cauchy integral representations and quadrature of the integral operators}
\label{appendix:A}

\edit{Here we convert the Stokes double-layer
  potential~\eqref{eqn:velocityDLP} and its derivatives to contour
  integrals around Jordan curves. We also provide quadrature formulas
  for each of these integrals.}
We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_2$ and use similar notation for $\yy$, $\nn$, and $\eeta$. We also interpret $\gamma$, the boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan curve in $\CC$. We introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)),
\end{align}
and define the five Cauchy integrals
\begin{align}
%  \label{eqn:cauchy_ints}
%  \begin{aligned}
  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\gamma}
  \frac{\Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
%  \end{aligned}
\end{align}
Then, the first and second components of the Stokes double-layer
  potential~\eqref{eqn:velocityDLP} are
\begin{subequations}
  \begin{align}
    u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
             \Re(v_3'(x)) + \Re(v_4(x)), \\
    u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
             \Im(v_3'(x)) + \Re(v_5(x)),
  \end{align}
  \label{eqn:velocityCauchy}
\end{subequations}
respectively. \edit{The deformation tensor is found by differentiating
  equation~\eqref{eqn:velocityCauchy}, and}
%  The components of the deformation tensor are
%\begin{subequations}
%  \begin{align}
%    \pderiv{u_1}{x_1} &= -\Re(v'_1(x)) + \Re(v''_3(x)) + \Re(v'_4(x))
%                         -\Re(x)\Re(v''_1(x)) - \Im(x)\Re(v''_2(x)) \\
%    \pderiv{u_1}{x_2} &= -\Re(v'_2(x)) - \Im(v''_3(x)) - \Im(v'_4(x))
%                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
%    \pderiv{u_2}{x_1} &= +\Im(v'_1(x)) - \Im(v''_3(x)) + \Re(v'_5(x))
%                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
%    \pderiv{u_2}{x_2} &= +\Im(v'_2(x)) - \Re(v''_3(x)) - \Im(v'_5(x))
%                         +\Re(x)\Re(v''_1(x)) + \Im(x)\Re(v''_2(x)) 
%  \end{align}
%  \label{eqn:deformationCauchy}
%\end{subequations}
%Having the deformation tensor at hand, 
the vorticity satisfies~\cite{chiu2020viscous}
%\begin{align}
%  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
%     \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
%  \label{eqn:vorticityCauchy}
%\end{align}
\begin{align}
  \omega(x) = \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
  \label{eqn:vorticityCauchy}
\end{align}
We note that the deformation tensor requires second-order derivatives of
Cauchy integrals, while the vorticity only requires first-order
derivatives. On solid boundaries, the vorticity reduces to the shear
stress given in~\eqref{tau0} and needed in erosion
law~\eqref{Vn0}~\cite{quaife2018boundary, chiu2020viscous}.

\edit{The overall accuracy of our method is determined by the accuracy
of the quadrature methods used to compute $v_i(x)$, $i=1,\ldots,5$, and
their first and second derivatives. Each $v_i(x)$ is a Cauchy integral
with the generic form}
\begin{align}
  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
  \label{eqn:cauchy1}
\end{align}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\subsection{Quadrature for Cauchy integrals}
%The overall accuracy of our method is determined by the
%quadrature rule applied to equation~\eqref{eqn:FredBIE}. Since we have
%written the Stokes double-layer potential
%velocity~\eqref{eqn:velocityCauchy}, deformation
%tensor~\eqref{eqn:deformationCauchy}, and
%vorticity~\eqref{eqn:vorticityCauchy} as a sum of Cauchy integrals and
%their derivatives, the overall accuracy hinges on the computation of a general Cauchy integral
%\begin{align}
%  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
%  \label{eqn:cauchy1}
%\end{align}
Here we describe a quadrature formula that was first used to approximate
analytic functions~\cite{ioa-pap-per1991}, and then extended to Stokes
layer potentials~\cite{bar-wu-vee2015}. The quadrature method requires
the boundary data of the analytic function~\eqref{eqn:cauchy1} which
satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} 
    \edit{\frac{1}{2\pi i}} \int_{\gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x_0-y} \, dy,
    \quad x_0 \in \gamma,
    \label{eqn:SP}
\end{align}
where the last integral is interpreted in the principal-value sense.
Here we are assuming that $\Omega$ is the bounded region interior to
$\gamma$. Once $v^{-}$ is calculated, $v(x)$ and its derivatives 
\edit{can be approximated by applying the trapezoid rule to the Cauchy
Integral Theorem. For example,
\begin{align}
  v(x) &= \frac{1}{2\pi i}\int_{\gamma} \frac{v^{-}(y)}{y-x} \,dy \approx 
    \frac{1}{2\pi i} \sum_{j=1}^{N} w_j \frac{v^{-}(y_j)}{y_j - x},
  \label{eqn:cauchyv}
\end{align}
}
%\begin{subequations}
%  \label{eqn:cauchy}
%  \begin{alignat}{3}
%  \label{eqn:cauchyv}
%  v(x) &= \frac{1}{2\pi i}\int_{\gamma} 
%    \frac{v^{-}(y)}{y-x} \,dy, \\
%  v'(x) &= \frac{1}{2\pi i} \int_{\gamma}
%    \frac{v^{-}(y)}{(y-x)^2} \, dy, \\
%  v''(x) &= \frac{1}{\pi i} \int_{\gamma}
%    \frac{v^{-}(y)}{(y-x)^3} \, dy.
%  \end{alignat}
%\end{subequations}
%The trapezoid rule can be used to approximate this Cauchy integral and
%its derivatives. For example, the Cauchy integral~\eqref{eqn:cauchyv}
%can be approximated as
%\begin{align}
%  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^{N} 
%    w_j \frac{v^{-}(y_j)}{y_j - x},
%  \label{eqn:trap}
%\end{align}
where $y_j$ are equispaced points on $\gamma$, $w_j = L/N$, and $L$ is
the length of $\gamma$. Because the integrand is both periodic and
smooth, given a fixed point $x$, the trapezoid rule achieves spectral
accuracy~\cite{tre-wei2014}. However, for a fixed $N$, the quadrature
error is not bounded uniformly with respect to $x$ because the
derivative of the integrand grows without bound as $x$ approaches
$\gamma$. This error is problematic for many of our simulations since we
allow eroding bodies to be arbitrarily close to one another, and we
often compute the velocity and vorticity at points in the fluid domain
that are close to an eroding body. In contrast to the integrand in the
Cauchy integral~\eqref{eqn:cauchyv}, the integrand in the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\gamma} 
    \frac{v^{-}(y) - v(x)}{y-x} \, dy = 0, \quad x \in \Omega,
  \label{eqn:trap2}
\end{align}
is bounded with respect to $x$, and therefore the error of the trapezoid
rule is bounded with respect to $x$. Applying the trapezoid rule, we
have
\begin{align}
  \frac{1}{2\pi i}\sum_{j=1}^{N} w_{j} 
    \frac{v^{-}(y_j) - v(x)}{y_j - x} \approx 0,
\end{align}
where the error is now uniformly bounded for all $x$. Rearranging, we
have
\begin{align}
  v(x) \approx \left(\frac{1}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}(y_j)}{y_j - x} w_j \right) \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j - x} w_j \right), 
  \quad x \in \Omega.
  \label{eqn:vBary}
\end{align}
Note that the numerator in~\eqref{eqn:vBary} is identical to \edit{the
approximation in}
equation~\eqref{eqn:cauchyv}, while the denominator is an approximation of
the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the errors
in the numerator and denominator grow, however, since the integrand in
equation~\eqref{eqn:trap2} is bounded independent of $x$, the error of
the ratio is also bounded independent of $x$.

The derivatives of the Cauchy integral in~\eqref{eqn:cauchy1},
\edit{which are need to compute the vorticty and deformation tensor,}
can be approximated with spectral accuracy, uniformly in $x$, using
similar quadrature rules. To summarize, for $x \in \Omega$, 
\begin{align}
  v'(x) &\approx \left(\frac{1}{2\pi i}\sum_{j=1}^{N}
    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j \right)
  \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^{N} \frac{1}{y_j-x} w_j\right), 
  \label{eqn:D1vBary} \\
  v''(x) &\approx \left(\frac{2}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j \right)
    \Bigg/
    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right),
  \label{eqn:D2vBary}
\end{align}
We note that equations~\eqref{eqn:vBary},~\eqref{eqn:D1vBary},
and~\eqref{eqn:D2vBary} all assume that $x \in \Omega$, where $\Omega$
is the bounded region interior to the Jordan curve $\gamma$. However, in
our application, when $\gamma$ is one of the eroding bodies, $x$ is in
the exterior region of the Jordan curve. In this case, slightly
different identities are used, but they all guarantee that the trapezoid
rule achieves spectral accuracy with an error that is independent of
$x$. A complete description of the quadrature rules
for~\eqref{eqn:vBary} and~\eqref{eqn:D1vBary} are described by Barnett,
Wu, and Veerapaneni~\cite{bar-wu-vee2015}, and the quadrature rule
for~\eqref{eqn:D2vBary} is described in our previous
work~\cite{chiu2020viscous}.

\end{appendices}

\end{document}
